Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Verification

### 2016-01-16 documentation/userguide.tex
Updated note on networks

For the nuclear network we use the \texttt{aprox13} network provided by Frank Timmes, which 
we have ported for use in the \texttt{Microphysics} repository. It is an alpha-chain network 
with isotopes ranging from ${}^4$He to ${}^{56}$Ni.

@@

If you want to build your own problem setup, you can do that too. The job submission 
requirements are the same as in Section \ref{sec:standard_problems}, but you will need to provide 
your own source files and makefile. They can go in the \texttt{compile/} subdirectory in your problem location.
At minimum, you'll need a \texttt{Prob\_3d.f90} file (or the equivalent for lower dimensions) and
corresponding inputs and probin files. The problems in \texttt{science/wdmerger_I/castro} are similar to this;
they are ultimately building using the source code in the CASTRO test suite, but using a
\texttt{run\_test.sh} that is very similar to the one used for merger problems.

@@

The \texttt{science/wdmerger_I/} directory contains a number of example problems that we use
to assess the reliability of \texttt{CASTRO} in performing hydrodynamics simulations 
with self-gravity. This section includes a list of the existing problems 
as well as the instructions for building and running a problem.

>>>>

For the nuclear network we use by default the \texttt{aprox13} network provided by Frank Timmes, which 
we have ported for use in the \texttt{Microphysics} repository. It is an alpha-chain network 
with isotopes ranging from ${}^4$He to ${}^{56}$Ni. We have also ported \texttt{aprox19} and
\texttt{aprox21}, which include the alpha chain isotopes as well as other nuclides for hydrogen
burning and more accurate iron-group calculations. It is also possible to use the \texttt{iso7}
network, which has the alpha nuclides from helium to silicon as well as nickel. The energy generation
rate will be less accurate but at least should give some qualitatively correct answers. You can also
provide your own network following the instructions in the Microphysics repository, as long as it
contains at least ${}^4$He, ${}^{12}$C, ${}^{16}$O, ${}^{20}$Ne, and ${}^{24}$Mg. This the minimum
set of isotopes needed to construct the initial white dwarf models.

@@

If you want to build your own problem setup, you can do that too. The job submission 
requirements are the same as in Section \ref{sec:standard_problems}, but you will need to provide 
your own source files and makefile. They can go in the \texttt{compile/} subdirectory in your problem location.
At minimum, you'll need a \texttt{Prob\_3d.f90} file (or the equivalent for lower dimensions) and
corresponding inputs and probin files. The problems in \texttt{science/wdmerger\_I/castro} are similar to this;
they are ultimately building using the source code in the CASTRO test suite, but using a
\texttt{run\_test.sh} that is very similar to the one used for merger problems. Note that for problems
in CASTRO/Exec, you'll need to append \texttt{CASTRO\_DIR=\$CASTRO\_DIR} to \texttt{make} at the
command line, which will force an override of that variable so that you can compile
outside of the root CASTRO directory.

@@

The \texttt{science/wdmerger\_I/} directory contains a number of example problems that we use
to assess the reliability of \texttt{CASTRO} in performing hydrodynamics simulations 
with self-gravity. This section includes a list of the existing problems 
as well as the instructions for building and running a problem.
